### 2015-05-26 fundamentals/fcsreqs.tex
Reviewer 1: "IB.iii: The simulation codes with discrete materials tracking are: COSI, FAMILY21, GENIUS 1 and 2, DANESS, NFCSim and ORION. DESAE doesn't. Not clear about VISION. DYMOND didn't neither." Removes DESAE.

Many fuel cycle phenomena have aggregate system-level effects which can only be
captured by discrete material tracking \cite{huff_next_2010}.  \Cyclus
tracks materials as discrete objects. Some current fuel cycle simulation tools
such as \gls{COSI}
\cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
\gls{DESAE}
\cite{andrianova_desae_2008}, FAMILY21\cite{mccarthy_benchmark_2012},
\gls{GENIUS} version 1, \gls{GENIUS} version 2, and \gls{NFCSim} also possess the ability to
model discrete materials.

>>>>

Many fuel cycle phenomena have aggregate system-level effects which can only be
captured by discrete material tracking \cite{huff_next_2010}.  \Cyclus
tracks materials as discrete objects. Some current fuel cycle simulation tools
such as \gls{COSI}
\cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
FAMILY21\cite{mccarthy_benchmark_2012},
\gls{GENIUS} version 1, \gls{GENIUS} version 2, \gls{NFCSim}, and ORION also 
possess the ability to model discrete materials.

### 2015-05-26 fundamentals/intro.tex
Thanks @gidden

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options.  The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the operational features of
nuclear energy systems, the dynamics of transitions between fuel cycles, and
many other measures of performance can be expressed in terms of these metrics.
For example, economic feasibility is often measured in \gls{LCOE}, requiring
calculation of lifetime fuel costs and electricity generation, while
environmental performance might be measured by spent fuel volume, toxicity, or
mined uranium.  A meta-analysis of fuel cycle systems studies identified over
two dozen unique quantitative metrics spanning economics and cost,
environmental sustainability and waste management impacts, safety, security and
nonproliferation, resource adequacy and utilization, among others
\cite{flicker_evaluation_2014}. With few exceptions (e.g.
\cite{poinssot_assessment_2014}), these metrics are derived from mass balances
calculated by a fuel cycle simulator.

>>>>

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options.  The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the operational features of
nuclear energy systems, the dynamics of transitions between fuel cycles, and
many other measures of performance can be expressed in terms of these metrics.
For example, economic feasibility is often measured in \gls{LCOE}, requiring
calculation of lifetime fuel costs and electricity generation, while
environmental performance might be measured by spent fuel volume, toxicity, or
mined uranium.  A meta-analysis of fuel cycle systems studies identified over
two dozen unique quantitative metrics spanning economics and cost,
environmental sustainability and waste management impacts, safety, security and
nonproliferation, resource adequacy and utilization, among others
\cite{flicker_evaluation_2014}. With few exceptions these metrics are derived from 
mass balances and facility operation history calculated by a fuel cycle 
simulator. For example, where nuclear waste repository burden is derived from 
ejected fuel masses, water pollution or land use can be derived from facility 
operational histories (as in \cite{poinssot_assessment_2014}).
